Notes on agt

### 2024-08-14 agt/survey.tex
modes

The theory of a twisted fivebrane in this geometry admits the following description.
In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(X,\bV)$ where $\bV$ is the following super complex of holomorphic vector bundles
\beqn
\bV \;\;\;\left\{
\begin{tikzcd}
& \ul{-1} & \ul{0} \\
\ul{\text{even}} & \Omega^2_X \ar[r,"\del"] & \Omega^3_X \\
\ul{\text{odd}} & \Pi W  
\end{tikzcd} \right.
\eeqn
We will write Dolbeault valued fields of the bundle in the first line with the letter as~$\beta$ and in the bottom line as $\phi$.

@@

Turning on this deformation leads to the deformed perturbative phase space
\beqn
\begin{tikzcd}
\ul{-2} & \ul{-1} & \ul{0} \\
& \Omega^{0,\bu}(S, \lie{g}) \ar[dd,dotted,"\omega \wedge \del"] & \\
\Omega^{2,\bu}(S,\lie{g} \otimes L^{-1}) & & \Omega^{0,\bu}(S, \lie{g} \otimes L) \\
& \Omega^{2,\bu}(S, \lie{g}) & .
\end{tikzcd}
\eeqn
A more invariant way to construct this perturbative phase space is the following.
The non-degenerate invariant pairing determines a four-form $\kappa$ on $BG$.
This pulls back, along the evaluation map
\beqn
\op{ev} \colon S \times \op{Bun}_G(S) \to BG 
\eeqn
to a four-form on $S \times \op{Bun}_G(S)$.
Integration of the six-form $\omega \wedge \op{ev}^*\kappa$ along $S$ yields a two-form $\omega_{\kappa} = \int_S \omega \wedge \op{ev}^*\kappa$ on $\op{Bun}_G(S)$.
We can, in turn, further restrict this to a two-form on $\cM_{G}(S,L)$ that we will abusively still denote by $\omega_{\kappa}$.
The phase space is then the twisted cotangent bundle
\beqn
\T_{\omega_{\kappa}}^* \left(\cM_{G}(S,L) \right) .
\eeqn

@@

Let $S$ be a projective surface and $L_1,L_2,L_3$ line bundles on $S$ satisfying 
\beqn
L_1 \otimes L_2 \otimes L_3 = K_S .
\eeqn
We consider a special case of the geometry (2) where the threefold that twisted fivebranes $X$ is of the form
\beqn
X = \op{Tot} \begin{pmatrix} L_3 \\ \downarrow \\ S \end{pmatrix},
\eeqn
and where $W = L_1 \oplus L_2$ (or rather, the restrictions of these line bundles to $X$).
In this case, the local Calabi--Yau fivefold geometry is $Z = \op{Tot}(L_1 \oplus L_2 \oplus L_3).$
\end{document}

>>>>

The theory of a twisted fivebrane in this geometry admits the following description.
In the Poisson BV formalism its sheaf of fields is of the form $\Omega^{0,\bu}(X,\bV)$ where $\bV$ is the following super complex of holomorphic vector bundles
\beqn\label{eqn:fivebranes}
\bV \;\;\;\left\{
\begin{tikzcd}
& \ul{-1} & \ul{0} \\
\ul{\text{even}} & \Omega^2_X \ar[r,"\del"] & \Omega^3_X \\
\ul{\text{odd}} & \Pi W  
\end{tikzcd} \right.
\eeqn
We will write Dolbeault valued fields of the bundle in the first line with the letter as~$\beta$ and in the bottom line as $\phi$.

@@

Turning on this deformation leads to the deformed perturbative phase space
\beqn
\begin{tikzcd}
\ul{-2} & \ul{-1} & \ul{0} \\
& \Omega^{0,\bu}(S, \lie{g}) \ar[dd,dotted,"\omega \wedge \del"] & \\
\Omega^{2,\bu}(S,\lie{g} \otimes L^{-1}) & & \Omega^{0,\bu}(S, \lie{g} \otimes L) \\
& \Omega^{2,\bu}(S, \lie{g}) & .
\end{tikzcd}
\eeqn
A more invariant way to construct this perturbative phase space is the following.
The non-degenerate invariant pairing determines a four-form $\kappa$ on $BG$.
This pulls back, along the evaluation map
\beqn
\op{ev} \colon S \times \op{Bun}_G(S) \to BG 
\eeqn
to a four-form on $S \times \op{Bun}_G(S)$.
Integration of the six-form $\omega \wedge \op{ev}^*\kappa$ along $S$ yields a two-form $\omega_{\kappa} = \int_S \omega \wedge \op{ev}^*\kappa$ on $\op{Bun}_G(S)$.
We can, in turn, further restrict this to a two-form on $\cM_{G}(S,L)$ that we will abusively still denote by $\omega_{\kappa}$.
The phase space is then the twisted cotangent bundle

\beqn\label{eqn:5dphase}
\T_{\omega_{\kappa}}^* \left(\cM_{G}(S,L) \right) .
\eeqn

@@

Let $S$ be a projective surface and $L_1,L_2,L_3$ line bundles on $S$ satisfying 
\beqn
L_1 \otimes L_2 \otimes L_3 = K_S .
\eeqn
We consider a special case of the geometry (2) where the threefold that twisted fivebranes $X$ is of the form
\beqn
X = \op{Tot} \begin{pmatrix} L_3 \\ \downarrow \\ S \end{pmatrix},
\eeqn
and where $W = L_1 \oplus L_2$ (or rather, the restrictions of these line bundles to $X$).
In this case, the local Calabi--Yau fivefold geometry is $Z = \op{Tot}(L_1 \oplus L_2 \oplus L_3).$

We will consider a variant of the factorization algebra $\Obs_{S, W}$ in the case where $L_3$ is possibly a nontrivial line bundle. Indeed, BV quantization of the fields \eqref{eqn:fivebrane} of a twisted fivebrane on $X$ yields a holomorphic factorization algebra $\Obs_{X, W}$ that specializes to $\Obs_{S, W}$ in the case where $L_3$ is the trivial line bundle on $S$ \surya{introduce earlier}

From the factorization algebra $\Obs_{X, W}$, we will produce a pair of an associative algebra and a module. To do so, we choose a Hermitian metric on $L_3$. Doing so gives us a norm map

\beqn
X\to X\times_S X \to S\times \C
\eeqn

which factors through the trivial $\R_{\geq 0}$-bundle on $S$ since a Hermitian metric is in particular positive definite. Let $p$ denote the composition of this map with the projection onto $\R_{\geq 0}$.

The geometry of the situation can be summarized in the following diagram

\[
\begin{tikzcd}
X\setminus S \ar[d,"\mathring p"'] \ar[r,hook] & X \ar[d,"p"] & \ar[l,hook',"0"'] S \ar[d] \\
\R_{>0} \ar[r,hook] & \R_{\geq 0} & \ar[l,hook'] \{0\}.
\end{tikzcd}
\]

The pushforward
\beqn
p_* \Obs_{X,W}
\eeqn

is therefore a factorization algebra on $\R_{\geq 0}$.

We may extract from this data, an associative algebra and a module as follows.

\begin{itemize}
\item Let $(a,b)\subset \R_{\geq 0}$. The sections $(p_* \Obs_{X, W})(a,b)$ are an associative algebra, which we will denote as $\AA(X, W)$.

This associative algebra can equivalently be computed by restricting away from $S$, and pushing forward along $\mathring p$. The fiber of this map at $r \in \R_{>0}$ is a copy of $S_r(L_3)\subset X$, the total space of the radius $r$ circle bundle in $L_3$. Notice that in the case when $L_3$ is trivial, this associative algebra is exactly the modes algebra of the vertex algebra $\VV_{S,W}$.

\item The costalk at zero $(p_*\Obs{X,W})_0$ is a module, which we denote as $\MM (X, W)$. 
\end{itemize}

The AGT relation asserts that $\MM(X,W)$ may equivalently be computed as the geometric quantization of \eqref{eqn:5dphase}

\end{document}
